Tuning for Software Analytics: is it Really Necessary?

### 2015-08-20 tuningpredictor.tex
test
move .eps into eps folder

\begin{figure}[!t]
\begin{center}
\includegraphics[width=1.5in]{precision_W.eps}\includegraphics[width=1.5in]{F_W.eps}
 \end{center}
\caption{Deltas in performance  seen in \tab{precisionbars} (left)
and \tab{fbars} (right) between tuned and untuned learners. Tuning improves performance when the deltas are above zero.}\label{fig:deltas}
 \end{figure}

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=1.5in]{LR_untuned.eps}\includegraphics[width=1.5in]{LR_tuned.eps}
 \end{center}
\caption{Comparison between Logistic Regression and Random Forests before and after tuning. }\label{fig:lr}
 \end{figure}

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=1.5in]{np_precision.eps}\includegraphics[width=1.5in]{np_f.eps}
 \end{center}
\caption{Deltas in performance between {\em np = 10} and the recommended np's. The recommended np is better when deltas are above zero. {\em np = 90, 50 and 60} are recommended population size for WHERE, CART and Random Forest by Storn.}\label{fig:deltas_np}
 \end{figure}

@@

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=1.5in]{features_precision.eps}\includegraphics[width=1.5in]{features_F.eps}
 \end{center}
\caption{Four representative tuning values in WHERE with  precision and F as the tuning goal, respectively.   }\label{fig:features}
 \end{figure}

>>>>

\begin{figure}[!t]
\begin{center}
\includegraphics[width=1.5in]{./eps/precision_W.eps}\includegraphics[width=1.5in]{./eps/F_W.eps}
 \end{center}
\caption{Deltas in performance  seen in \tab{precisionbars} (left)
and \tab{fbars} (right) between tuned and untuned learners. Tuning improves performance when the deltas are above zero.}\label{fig:deltas}
 \end{figure}

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=1.5in]{./eps/LR_untuned.eps}\includegraphics[width=1.5in]{./eps/LR_tuned.eps}
 \end{center}
\caption{Comparison between Logistic Regression and Random Forests before and after tuning. }\label{fig:lr}
 \end{figure}

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=1.5in]{./eps/np_precision.eps}\includegraphics[width=1.5in]{./eps/np_f.eps}
 \end{center}
\caption{Deltas in performance between {\em np = 10} and the recommended np's. The recommended np is better when deltas are above zero. {\em np = 90, 50 and 60} are recommended population size for WHERE, CART and Random Forest by Storn.}\label{fig:deltas_np}
 \end{figure}

@@

% \begin{table}[!t]
% \renewcommand{\baselinestretch}{0.8}
% \scriptsize
% \centering
%   \begin{tabular}{c|c |c}
%     &   \multicolumn{1}{c|}{Precision} & \multicolumn{1}{c}{F} \\ \hline 
%     Learner  & np = 10 & recommended np \\
% \hline
%     WHERE & 0.18 & 0.24 \\
%     CART  & 0.12 & 0.12  \\
%     R. Forest &  0.12 & 0.12 \\
%   \end{tabular}
%     \caption{Kolmogorov-Smirnov Tests for distributions of each learner with np = 10 and recommended np's }\label{tab:ks}
% \end{table}

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=1.5in]{./eps/features_precision.eps}\includegraphics[width=1.5in]{./eps/features_F.eps}
 \end{center}
\caption{Four representative tuning values in WHERE with  precision and F as the tuning goal, respectively.   }\label{fig:features}
 \end{figure}
